---
title: "Text Package Implementation and Testing"
output: html_notebook
---


```{r}
# Install Text from CRAN
#install.packages("text")
library(text)
```

```{r}
# Set-up environment with Text required python packages
#textrpp_install()

# Initialize the environment and save the settings for the next time
textrpp_initialize(save_profile = TRUE)
```
```{r}
# load test dataset
library(readr)
black <- read_csv("Source_data/blackCommunities.csv")

#filtering out mission statements containing the words -black, african-american, people of color, black communities
black <- black %>% filter(BLACK == 1)

#keeping only the required columns in both datasets
black <- select(black,mission,orgname)

#Renaming columns
black <- rename(black, Mission = mission, OrgName=orgname)
```


### Making word embeddings using BERT

```{r}
# Look at example data included in the text package comprising both text and numerical variables (note that there are only 292 mission statements in this test data).
head(black)
```

```{r}
# Transform the text/word data to word embedding.
#word_embeddings <-textEmbed(black, model = "bert-base-uncased")

# Save the word embedding to avoid having to embed the text again. It is good practice to save output from analyses that take a lot of time to compute, which is often the case when analyzing text data.
#saveRDS(word_embeddings, "word_embeddings.rds")

# Get the saved word embedding (again)
word_embeddings <-readRDS("word_embeddings.rds")

```

```{r}
# Look at the word embeddings
#word_embeddings
```



### Calculating Semantic Similarity

1. Our Mission is to educate individuals from all walks of life and backgrounds about the history of African Americans and to examine and tell the stories of a still marginalized population in America Theater.  Guided by the Black Hollywood Legends (1)
2. a. educate both traditional and non-traditional theatre audiences as to the complexity, sophistication and relevance of black theatre b. to provide a home for theatre artists to practice their craft under professional conditions (3)
3. To provide a social forum to provide opportunities for rural West Tennesseans to perform blacksmithing. (45)
4. To provide blacksmithing, knifemakeing and metal working classes to veterans, and other underserved populations. (68)
5. Use travel to inspire and broaden educational and cultural experiences of people of colour (18)
6. The mission of Taking Travel Black is to build a community of global citizens from across the Black Diaspora. (28)            
7. The Black Marlins Swim will be a swim team based on the ideology that technique and consistency come before conditioning. (93)

```{r}
# Compute semantic similarity scores between two text columns, using the previously created word_embeddings.

# 1 and 2
textSimilarity(word_embeddings$Mission[1,],word_embeddings$Mission[2,])

# 3 and 4
textSimilarity(word_embeddings$Mission[45,],word_embeddings$Mission[68,])

# 1 and 68
textSimilarity(word_embeddings$Mission[1,],word_embeddings$Mission[68,])

# 2 and 45
textSimilarity(word_embeddings$Mission[2,],word_embeddings$Mission[45,])

# 1 and 93
textSimilarity(word_embeddings$Mission[93,],word_embeddings$Mission[1,])

# 45 and 18
textSimilarity(word_embeddings$Mission[18,],word_embeddings$Mission[45,])

# 28 and 18
textSimilarity(word_embeddings$Mission[18,],word_embeddings$Mission[28,])

```

### Questions to be addressed
- Model still needs to be improved
- Word embeddings for 292 mission statemnets took close to ~60 mins
- I'm doing pairwise similarity scores - convert this to more usable format
- Mapping embeddings back to non profit information

